Proposed Solution

### 2016-11-11 Ennan-Proposal/prelim.tex
stuff

From ConfigC we drew the main inspiration for this proposal. We now briefly
outline how does ConfigC work. It first automatically
analyzes datasets of correct configuration files, 
and then derives rules for building a language model 
from the given datasets.

The algorithm can be summarized as follows: we identified several basic types, 
such Boolean, Integer, File. With each of these files we associated a list 
of templates. We then analyze {\emph {correct}} configuration files. When we 
detect that a certain variable (or a pair of variable

\begin{figure}
	\centering
\begin{minipage}{0.9\textwidth}
\begin{parcolumns}{2}
\colchunk{\begin{lstlisting}[language=C, frame=tb, xleftmargin=.01\textwidth]
File 1:
max_connections=300
general_log=1
...
mysql.max_persistent=200
\end{lstlisting}}

\colchunk{\begin{lstlisting}[language=C, frame=tb, xleftmargin=.01\textwidth]
File 2:
max_connections=400
general_log=0
...
mysql.max_persistent=200
\end{lstlisting}}

\colplacechunks
\end{parcolumns}
\end{minipage}
	\caption{Fragments of two configuration files for configuring PHP on MySQL}
\end{figure}

The resulting language model, together with accompanying rules, 
is then used to detect errors in new configuration files.
ConfigC can detect the following errors in configuration files:
entry missing errors, ordering errors, type errors and
simple value correlation. Running ConfigC on Example~1 from 
Sec.~\ref{sec:intro-examples} returns the following output:
\begin{lstlisting}[language=C, xleftmargin=.01\textwidth]
ORDERING ERROR: Expected extension "recode.so" BEFORE 
extension "mysql.so"
\end{lstlisting} 
ConfigC could not detect an error present in Example~2 since it can detect 
only simple comparison-based relations.

>>>>

From ConfigC we drew the main inspiration for this proposal. We now briefly
outline how does ConfigC work on two configuration files given in 
Fig.~\ref{fig:twoFiles}. ConfigC first automatically
analyzes a dataset of correct configuration files to derive
 rules for describing a specification. Before that process even starts,
we identified several basic types, 
such Boolean, Integer, File. With each of these files we associated a list 
of templates. We then analyze {\emph {correct}} configuration files. When analyzing
a file, we first do type-checking, \ie we assign a type to every variable. 
We next instantiate each template with the typed variables and we save the learned set 
of rules. For instance, with integers we associate comparison templates, so after 
analyzing File$_1$, the set of learned rules will contain:
\begin{lstlisting}[language=C, xleftmargin=.01\textwidth]
max_connections=300
mysql.max_persistent=200
max_connections > mysql.max_persistent
\end{lstlisting}
The set of learned rules is changing with every file that we analyze: contradicting 
files are removed and new rules are added. In practice, this process is done 
in parallel.

After analyzing File$_2$ the rule \texttt{max\_connections = 300} is removed.

\begin{figure}
	\centering
\begin{minipage}{0.9\textwidth}
\begin{parcolumns}{2}
\colchunk{\begin{lstlisting}[language=C, frame=tb, xleftmargin=.01\textwidth]
File_1:
max_connections=300
general_log=1
...
mysql.max_persistent=200
\end{lstlisting}}

\colchunk{\begin{lstlisting}[language=C, frame=tb, xleftmargin=.01\textwidth]
File_2:
max_connections=400
general_log=0
...
mysql.max_persistent=200
\end{lstlisting}}

\colplacechunks
\end{parcolumns}
\end{minipage}
	\caption{Fragments of two configuration files for configuring PHP on MySQL}
	\label{fig:twoFiles}
\end{figure}

Once this preprocessing of training data is done, the resulting language model, 
together with accompanying rules, 
is used to detect errors in new configuration files given by the user.

Additional to the described process we also developed algorithms for the 
misconfigurations that cannot easily be templated. All together, ConfigC 
can detect the following errors:
missing entries, ordering errors, type errors and
simple value correlations. Running ConfigC on Example~1 from 
Sec.~\ref{sec:intro-examples} returns the following output:
\begin{lstlisting}[language=C, xleftmargin=.01\textwidth]
ORDERING ERROR: Expected extension "recode.so" BEFORE 
extension "mysql.so"
\end{lstlisting} 
ConfigC could not detect an error present in Example~2 since it can detect 
only simple comparison-based relations.
